Modeling thermal dust emission with two components: application to the {\it PLANCK} HFI maps

### 2014-08-09 ms.tex
improvements to several figure captions

\begin{figure*}
\begin{center}
\epsfig{file=posteriors.eps, width=7.0in}
\caption{\label{fig:post} Gridded posterior PDFs for three $N_{side}$=2048 
pixels, based on \PLANCK~217-857 GHz and SFD 100$\mu$m at full $6.1'$ 
resolution. The colorscale is linear in $log(P)$, with black corresponding to 
the maximum of $log(P)$ and white representing $max[log(P)]-5$. Light green 
crosses and ellipses mark the best-fit parameters and $1\sigma$ uncertainties 
based on our MCMC sampling of the posteriors. Our MCMC parameter and 
uncertainty estimates are in good agreement with those based on gridded 
posteriors. These three pixels are also representative in that we find the 
posterior distributions from Equation \ref{eqn:post} are in general extremely 
well-behaved, showing no multimodality or other pathological qualities. Left: 
Low S/N pixel at high latitude in the Galactic north. Center: High S/N pixel in
the Polaris flare region. Right: Low S/N pixel at high latitude in the Galactic
south.}
\end{center}
\end{figure*}

@@

\begin{figure}
\begin{center}
\epsfig{file=f1_1deg.eps, width=3.3in}
\caption{\label{fig:f1} $1^{\circ}$ FWHM full-sky map of $f_1$ derived from our
low-resolution fits described in $\S$\ref{sec:lores}. Red coloring masks pixels
with appreciable molecular emission, as defined in $\S$\ref{sec:mole}. Such 
pixels should not be trusted in this analysis, which is sensitive to the SED 
shape at low frequencies affected by CO line emission. Variations in $f_1$
along the ecliptic plane are spurious results of imperfect zodiacal light
subtractions. However, interesting astrophysical variations of $f_1$ 
are evident, particularly the trend of increasing $f_1$ with decreasing
Galactic latitude, the relatively low $f_1$ values in the Polaris flare region,
and the clouds with relatively high $f_1$ values the north Galactic pole.}
\end{center}
\end{figure}

@@

The resulting full-sky map of $f_1$ is shown in Figure \ref{fig:f1}. A 
general trend of increasing $f_1$ towards lower Galactic latitudes is 
apparent. The other most salient features are the relatively low
values of $f_1$ in the Polaris flare, and the relatively high $f_1$ clouds
near the north Galactic pole.

@@

\begin{figure}
\begin{center}
\epsfig{file=chi2_dirbe.eps, width=3.3in}
\caption{\label{fig:chi2_dirbe} Comparison of goodness-of-fit, 
$\chi^2_{\nu}$=$\langle \chi^2_{p, \nu} \rangle$, for various dust SED models,
as described in $\S$\ref{sec:hier}. For single-MBB models with spatially 
constant $\beta$, we varied $\beta$ between 1 and 2 (horizontal axis), 
achieving reduced chi-squared $\chi^2_{\nu}$ shown by the black line, with 
$\beta$=1.57 providing the best fit. Horizontal lines indicate $\chi^2_{\nu}$ 
for other dust emission models considered, including the FDS99 best-fit 
two-component model (Table \ref{tab:global}, model 1, red) and the 
\cite{planckdust} single-MBB model (green). The minimum $\chi^2_{\nu}$ is 
achieved with two-componenent `model 2' from Table \ref{tab:global} (magenta).}
\end{center}
\end{figure}

@@

\subsection{Reddening Calibration Procedure}

\begin{figure}
\begin{center}
\epsfig{file=calib_ebv.eps, width=3.3in}
\caption{\label{fig:calib} Linear fit of $E(B-V)_{SSPP}$ as a function of
two-component $\tau_{545}$, illustrating our procedure for calibrating optical 
depth to reddening.}
\end{center}
\end{figure}

@@

\begin{figure*} [ht]
\begin{center}
\epsfig{file=results.eps, width=7.0in}
\caption{\label{fig:results} (top) Hot dust temperature derived from our 
full-resolution two-component model fits of \PLANCK~217-857 GHz and SFD 
100$\mu$m, downbinned to 27.5$'$ resolution. (bottom) Corresponding full-sky 
map of best-fit 545 GHz optical depth.}
\end{center}
\end{figure*}

>>>>

\begin{figure*}
\begin{center}
\epsfig{file=posteriors.eps, width=7.0in}
\caption{\label{fig:post} Gridded posterior PDFs for three $N_{side}$=2048 
HEALPix pixels, based on \PLANCK~217-857 GHz and SFD 100$\mu$m at full $6.1'$ 
resolution. The colorscale is linear in $log(P)$, with black corresponding to 
the maximum of $log(P)$ and white representing $max[log(P)]-5$. Light green 
crosses and ellipses mark the best-fit parameters and $1\sigma$ uncertainties 
based on our MCMC sampling of the posteriors. Our MCMC parameter and 
uncertainty estimates are in good agreement with those based on gridded 
posteriors. These three pixels are also representative in that we find the 
posterior distributions from Equation \ref{eqn:post} are in general extremely 
well-behaved, showing no multimodality or other pathological qualities. Left: 
Low S/N pixel at high latitude in the Galactic north. Center: High S/N pixel in
the Polaris flare region. Right: Low S/N pixel at high latitude in the Galactic
south.}
\end{center}
\end{figure*}

@@

\begin{figure}
\begin{center}
\epsfig{file=f1_1deg.eps, width=3.3in}
\caption{\label{fig:f1} $1^{\circ}$ FWHM full-sky map of $f_1$ derived from our
low-resolution fits described in $\S$\ref{sec:lores}. Red coloring masks pixels
with appreciable molecular emission, as defined in $\S$\ref{sec:mole}. Such 
pixels should not be trusted in this analysis, which is sensitive to the SED 
shape at low frequencies affected by CO line emission. Variations in $f_1$
along the ecliptic plane are spurious results of imperfect zodiacal light
subtractions. However, interesting astrophysical variations of $f_1$ 
are evident, particularly the trend of increasing $f_1$ with decreasing 
absolute Galactic latitude, the relatively low $f_1$ values in the Polaris 
flare region, and the clouds with relatively high $f_1$ values near the north 
Galactic pole.}
\end{center}
\end{figure}

@@

The resulting full-sky map of $f_1$ is shown in Figure \ref{fig:f1}. A 
general trend of increasing $f_1$ towards lower absolute Galactic latitudes is 
apparent. The other most salient features are the relatively low
values of $f_1$ in the Polaris flare, and the relatively high $f_1$ clouds
near the north Galactic pole.

@@

\begin{figure}
\begin{center}
\epsfig{file=chi2_dirbe.eps, width=3.3in}
\caption{\label{fig:chi2_dirbe} Comparison of goodness-of-fit, 
$\chi^2_{\nu}$=$\langle \chi^2_{p, \nu} \rangle$, for various dust SED models,
as described in $\S$\ref{sec:hier}. For single-MBB models with spatially 
constant $\beta$, we varied $\beta$ between 1 and 2 (horizontal axis), 
achieving reduced chi-squared $\chi^2_{\nu}$ shown by the black line, with 
$\beta$=1.57 providing the best single-MBB fit. Horizontal lines indicate 
$\chi^2_{\nu}$ for other dust emission models considered, including the FDS99 
best-fit two-component model (Table \ref{tab:global}, model 1, red) and the 
\cite{planckdust} single-MBB model (green). The minimum $\chi^2_{\nu}$ is 
achieved with two-componenent `model 2' from Table \ref{tab:global} (magenta).}
\end{center}
\end{figure}

@@

\subsection{Reddening Calibration Procedure}
\label{sec:calib_ebv}

\begin{figure}
\begin{center}
\epsfig{file=calib_ebv.eps, width=3.3in}
\caption{\label{fig:calib} Linear fit of $E(B-V)_{SSPP}$ as a function of
two-component 545 GHz optical depth, illustrating our procedure for 
calibrating optical depth to reddening, as described in 
$\S$\ref{sec:calib_ebv}.}
\end{center}
\end{figure}

@@

\begin{figure*} [ht]
\begin{center}
\epsfig{file=results.eps, width=7.0in}
\caption{\label{fig:results} (top) Hot dust temperature derived from our 
full-resolution two-component model fits of \PLANCK~217-857 GHz and SFD 
100$\mu$m, downbinned to 27.5$'$ resolution. (bottom) Corresponding full-sky 
map of best-fit two-component 545 GHz optical depth.}
\end{center}
\end{figure*}
